### 2021-04-08 papers/SYRCoSE/related.tex

More recently event structures were applied 
in the context of relaxed memory models~%
\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19, Moiseenko-al:ECOOP20}.
Among this line of work, we are aware of only one paper~\cite{Moiseenko-al:ECOOP20}
that was accompanied with a mechanisation in a proof assistant. 
The authors formalised \weakestmo~\cite{Chakraborty-Vafeiadis:POPL19} 
memory memory model in \coq. However, this memory model uses 
a custom variant of event structures, that does not 
obey axioms of any conventional class of 
event structures~\cite{Winskel:82, Langerak:91, Boudol-Castellani:1991}. 
This fact makes it harder to reuse and adapt it 
to other applications of the theory.

>>>>

More recently event structures were applied 
in the context of relaxed memory models~%
\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19, Moiseenko-al:ECOOP20}.
Among this line of work, we are aware of only one paper~\cite{Moiseenko-al:ECOOP20}
that was accompanied with a mechanisation in a proof assistant. 
The authors formalised \weakestmo~\cite{Chakraborty-Vafeiadis:POPL19} 
memory model in \coq. However, this memory model uses 
custom variant of event structures, that does not 
obey axioms of any conventional class of 
event structures~\cite{Winskel:82, Langerak:91, Boudol-Castellani:1991}. 
This fact makes it harder to reuse and adapt it 
to other applications of the theory.
